Beef Pricing Dynamics in the Canadian Grocery Market: A Comparative Analysis of Walmart and T&T

### 2024-11-28 paper/paper.qmd
parquet data modified, citation updated

```{r}
#| include: false
#| warning: false
#| message: false
# load library
package_list <- c("tidyverse", "kableExtra", "ggplot2", "dplyr", "here", "knitr", "rstanarm", "modelsummary", "readr", "lme4", "tinytex", "reshape2")

@@

# load data
ppu_data <- read_csv(here("data", "02-analysis_data", "ppu_data.csv"), show_col_types = FALSE)
beef_data <- read_csv(here("data", "02-analysis_data", "beef_data.csv"), show_col_types = FALSE)

@@

This project is motivated and guided by Rohan Alexander and his book [@citeTbook]. Data used in this paper was cleaned, analyzed and modeled with the programming language R [@citeR]. Also with support of additional packages in R: `readr` [@citeReadr], `ggplot2` [@citeGgplot2], `tidyverse` [@citeTidyverse], `dplyr` [@citeDplyr], `here` [@citeHere], `knitr` [@citeKnitr], `kableExtra` [@citeKableExtra], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModelsummary], `lme4` [@citeLme4], `tinytex` [@citeTinytex], `reshape2` [@citeReshape2].

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
# load library
package_list <- c("tidyverse", "kableExtra", "ggplot2", "dplyr", "here", "knitr", "rstanarm", "modelsummary", "readr", "lme4", "tinytex", "reshape2", "arrow")

@@

# load data
ppu_data <- read_parquet(here("data", "02-analysis_data", "ppu_data.parquet"))
beef_data <- read_parquet(here("data", "02-analysis_data", "beef_data.parquet"))

@@

This project is motivated and guided by Rohan Alexander and his book [@citeTbook]. Data used in this paper was cleaned, analyzed and modeled with the programming language R [@citeR]. Also with support of additional packages in R: `readr` [@citeReadr], `ggplot2` [@citeGgplot2], `tidyverse` [@citeTidyverse], `dplyr` [@citeDplyr], `here` [@citeHere], `knitr` [@citeKnitr], `kableExtra` [@citeKableExtra], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModelsummary], `lme4` [@citeLme4], `tinytex` [@citeTinytex], `reshape2` [@citeReshape2], `arrow` [@citeArrow].
